\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\title{Expanding Flicker30k: a Novel Dataset for Image Captioning in Persian}

\author{Shima Baniadamdizaj}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2021}%
{Shell \MakeLowercase{\textit{et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}

\IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

\maketitle

\begin{abstract}
  Image captioning, the challenge of describing images through natural language, particularly benefits from deep learning techniques which need diverse datasets. While existing datasets like Microsoft COCO and Flickr30k offer valuable resources, they are predominantly in English. The Expanding Flicker30k dataset fills this void for the Persian language. With manually curated captions averaging 13.3 words, the dataset captures various visual scenarios. By addressing the absence of Persian captioning resources, this paper contributes to both image captioning and multi-lingual research, fostering improved image understanding and language generation capabilities.
  This paper presents a novel resource for Persian language image captioning. Built upon the Flickr30k dataset, the new collection comprises 51,000 captions corresponding to 10,200 distinct images, providing a crucial dataset for advancing image captioning research in the Persian language. Each picture has five captions in Persian, which helps overcome the lack of non-English captioning datasets and allows for detailed language analysis. The dataset includes columns for image names, comment numbers, Persian captions, and English translations, facilitating bilingual comparisons.
\end{abstract}

\begin{IEEEkeywords}
  Image Captioning in Persian \and Computer Vision \and Natural language processing \and image-to-text.
\end{IEEEkeywords}


\end{document}


